%Copyright 2014 Jean-Philippe Eisenbarth
%This program is free software: you can
%redistribute it and/or modify it under the terms of the GNU General Public
%License as published by the Free Software Foundation, either version 3 of the
%License, or (at your option) any later version.
%This program is distributed in the hope that it will be useful,but WITHOUT ANY
%WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
%PARTICULAR PURPOSE. See the GNU General Public License for more details.
%You should have received a copy of the GNU General Public License along with
%this program.  If not, see <http://www.gnu.org/licenses/>.

%Based on the code of Yiannis Lazarides
%http://tex.stackexchange.com/questions/42602/software-requirements-specification-with-latex
%http://tex.stackexchange.com/users/963/yiannis-lazarides
%Also based on the template of Karl E. Wiegers
%http://www.se.rit.edu/~emad/teaching/slides/srs_template_sep14.pdf
%http://karlwiegers.com
\documentclass{scrreprt}
\usepackage{listings}
\usepackage{underscore}
\usepackage[bookmarks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{longtable}
\hypersetup{
    bookmarks=false,    % show bookmarks bar?
    pdftitle={Software Requirement Specification},    % title
    pdfauthor={Jean-Philippe Eisenbarth},                     % author
    pdfsubject={TeX and LaTeX},                        % subject of the document
    pdfkeywords={TeX, LaTeX, graphics, images}, % list of keywords
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,       % color of internal links
    citecolor=black,       % color of links to bibliography
    filecolor=black,        % color of file links
    urlcolor=purple,        % color of external links
    linktoc=page            % only page is linked
}%
\def\myversion{1.0 }
\date{}
%\title{%

%}
\usepackage{hyperref}
\begin{document}

\begin{flushright}
    \rule{16cm}{5pt}\vskip1cm
    \begin{bfseries}
        \Huge{SOFTWARE REQUIREMENTS\\ SPECIFICATION}\\
        \vspace{1.9cm}
        for\\
        \vspace{1.9cm}
        GBUS Scheduling App\\
        \vspace{1.9cm}
        \LARGE{Version \myversion approved}\\
        \vspace{1.9cm}
        Prepared by Jack Doiron, Jared Cassarly, Shota Nemoto, Martin Peters\\
        \vspace{1.5cm}
        GBUS!LLC\\
        \vspace{1.5cm}
        \today\\
    \end{bfseries}
\end{flushright}

\tableofcontents


\chapter*{Revision History}

\begin{center}
    \begin{tabular}{|c|c|c|c|}
        \hline
	    Name & Date & Reason For Changes & Version\\
        \hline
	    21 & 22 & 23 & 24\\
        \hline
	    31 & 32 & 33 & 34\\
        \hline
    \end{tabular}
\end{center}

\chapter{Introduction}

\section{Purpose}
This document describes the requirements for the GBUS Scheduling Application version 1.0.  This document is intended to be used for reference by the developers of the application.

\section{Vision Statement}
The application will be a standard scheduler/calendar. The goal of this project is to give the user a standard calendar experience while streamlining their ability to schedule and modify events.  We want to improve upon the user experience when using a calendar so that the user can manage their time more effectively with less overhead. Additionally, the application will be cross platform, allowing the user to manage their schedule on all of their devices.\\

\section{Major Features}
\begin{center}
\begin{tabular}{  p{1cm}  p{13cm}  }
FE-1: & The user has the ability to view a graphical representation of their schedule.\\
FE-2: & The user can create Standard, Location, and Deadline events with parameters defined by the user.\\
FE-3: & User can modify any of their scheduled events.\\
FE-4: & The user can request the application to automatically schedule deadline events and resolve event conflicts.\\
FE-5: & The user will be able to use a editing toolbar to easily modify their events.\\
FE-6: & The user will be able to sync their calendar data across devices.\\
FE-7: & The user will be able to change application settings and view account information\\
\end{tabular}
\end{center}

\section{Dependencies}
\begin{center}
\begin{tabular}{  p{1cm}  p{13cm}  }
DE-1: & The user must have internet connection in order to utilize calendar synchronization.\\
\end{tabular}
\end{center}


\section{References}
Airbnb. \textit{Airbnb Javascript Style Guide() \{},\\ https://github.com/airbnb/javascript

\chapter{Overall Description}

\section{Operating Environment}
\begin{center}
\begin{longtable}{ p{1cm} p{14cm} }
OE-1: & The GBUS application shall operate on the following platforms: The latest version of Google Chrome, Android version 7, iPhone versions 7, 8, and X. \\
OE-2: & The GBUS application shall store all user account data on a server running the latest Debian Linux and will be moved to Amazon Web Services for production. \\
\end{longtable}
\end{center}

\section{Design and Implementation Constraints}
\begin{center}
\begin{longtable}{ p{2cm} p{13cm} }
CO-1: & All JavaScript code shall conform to the \textit{Airbnb Javascript Style Guide() \{} \\
\end{longtable}
\end{center}

\section{User Documentation}
The user documentation includes:
\begin{itemize}
    \item General help page\newline
    This page will provide links to other help pages specialized for particular
    features as well as answers to frequently asked questions.
    \item Event creation help page\newline
    This page will contain a step-by-step procedure of how to create events
    and pictures of the relevant sections of the user interface.
    \item Event editing help page\newline
    This page will contain typical sequences for editing event attributes. It
    includes information about the editing toolbar as well as editing events
    from the event information screen.
    \item Auto-scheduling help page\newline
    This page will contain information about how the auto-scheduler identifies
    time-slots to place its events as well as how each setting alters its behavior.
\end{itemize}


\chapter{External Interface Requirements}

\section{User Interfaces}
There are three different interfaces. The primary interface is the calendar page, which displays 4 weeks, starting with the first week in the current month. On this page the toolbar is placed next to the calendar, with editing tools for the calendar as well as access to the general settings page on it. The calendar page will allow the user to drag and drop events into new locations on the calendar. The second interface is the event editing page, accessible by double-clicking or tapping on an event. The event editing page is in list format, with each point corresponding to an editable trait of the event, which the user is able to edit from either a drop-down menu or a text box, depending on the trait. The third user interface is the general settings page, which is laid out in list format, and the items in that list are enumerated in the general settings section.



\section{Hardware Interfaces}
$<$Describe the logical and physical characteristics of each interface between
the software product and the hardware components of the system. This may include
the supported device types, the nature of the data and control interactions
between the software and the hardware, and communication protocols to be
used.$>$

\section{Software Interfaces}
\begin{center}
\begin{tabular}{  p{1cm}  p{13cm}  }
SI-1: & \textit{Create React App} was used to initialize the web environment and \textit{React Native CLI} was used to initialize the native environment.\\
SI-2: & The application relies on the \textit{React}, \textit{React Native}, and \textit{ReactDOM} for interacting with the user interface.\\
SI-3: & The application relies on \textit{Redux} to manage and update state information.
\end{tabular}
\end{center}

\section{Communications Interfaces}
$<$Describe the requirements associated with any communications functions
required by this product, including e-mail, web browser, network server
communications protocols, electronic forms, and so on. Define any pertinent
message formatting. Identify any communication standards that will be used, such
as FTP or HTTP. Specify any communication security or encryption issues, data
transfer rates, and synchronization mechanisms.$>$


\chapter{System Features}
$<$This template illustrates organizing the functional requirements for the
product by system features, the major services provided by the product. You may
prefer to organize this section by use case, mode of operation, user class,
object class, functional hierarchy, or combinations of these, whatever makes the
most logical sense for your product.$>$

\section{General Settings}

\subsection{Description and Priority}
The General Settings menu of the application provides the user with options that allows them to customize their experience. All changes made in the menu will automatically save and sync with the server. Priority = Low.

\subsection{Stimulus/Response Sequences}
\begin{center}
\begin{longtable}{ p{2cm} p{13cm} }
Stimulus: & The user opens the General Settings menu. \\
Response: & All of the available options to customize are listed to the user with entry forms. \\
\\
Stimulus: & The user chooses the exit menu option. \\
Response: & The application returns to the calendar view. \\
\\
Stimulus: & The user enters a new default value into one of the entry forms in the General Settings menu. \\
Response: & The value used by the feature they are changing the setting for is updated within the application. The change is only used for future actions by the user.  No changes are automatically made to existing events. \\
\\
Stimulus: & The user attempts to enter a new value minimum or maximum event time value that does not fall into the proper constraints for the value. \\
Response: & The user is presented with an error and the application requests that they change the value to something valid.  No changes to the default used by the application are used and the changes the user made are not saved if they leave the menu and come back. \\
\\
Stimulus: & The user chooses to change their email or reset their password. \\
Response: & The application displays two new text fields under the selected option where the user enters their new email or password and then re-enters the same email or password.  Assuming both fields have matching text, the application updates the account with the new information on the server. \\
\\
Stimulus: & The user tries to login, logout, or register. \\
Response: & The appropriate synchronization menu is opened and the user follows the prompts there. \\
\end{longtable}
\end{center}

\subsection{Functional Requirements}
\begin{center}
\begin{longtable}{ | p{6cm} | p{9cm} | }
\hline
Settings.Exit & The General Settings menu shall have an option to leave the menu and return to the calendar. \\
\hline
Settings.Toolbar.SnapToGrid & The General Settings menu shall allow the user to set the default length of time that is used in the Toolbar's Snap to Grid feature. \\
& \\
Settings.Toolbar.SnapToGrid.Default & The default Snap to Grid time shall be set to 5 minutes until changed by the user. \\
\hline
Settings.AutoScheduling.Breaks & The General Settings menu shall allow the user to set time periods where no events are scheduled when using the Auto Scheduling feature. \\
& \\
Settings.AutoScheduling.MinTime & The General Settings menu shall allow the user to set the default minimum amount of time the auto scheduler will use when creating events. \\
& \\
Settings.AutoScheduling. MinTime.Constraints & The General Settings menu shall not allow the user to set a default minimum event time greater than the maximum event time. \\
& \\
Settings.AutoScheduling. MinTime.Default & The default maximum event time for the auto scheduler shall be set to 15 minutes until changed by the user. \\
& \\
Settings.AutoScheduling.MaxTime & The General Settings menu shall allow the user to set the default maximum amount of time the auto scheduler will use when creating events. \\
& \\
Settings.AutoScheduling.MaxTime. Constraints & The General Settings menu shall not allow the user to set a default maximum event time less than the minimum event time. \\
& \\
Settings.AutoScheduling.MaxTime. Default & The default maximum event time for the auto scheduler shall be set to 1 hour until changed by the user. \\
& \\
Settings.AutoScheduling. MinOpenTime & The General Settings menu shall allow the user to set the default minimum amount of time that must be between auto scheduled deadline events. \\
& \\
Settings.AutoScheduling. MinOpenTime.Default & The default minimum open time between deadline events for the auto scheduler shall be set to 15 hour until changed by the user. \\
\hline
Settings.Language & The General Settings menu shall allow the user to change the language localization from a list of available languages. \\
& \\
Settings.Language.Default & The default language localization used by the application shall be English. \\
\hline
Settings.Events.Notifications & The General Settings menu shall allow the user to set the default notifications from the following choices: banner, popup, off. \\
& \\
Settings.Events.Notifications.Default & The default notification setting shall be a banner by default \\
& \\
Settings.Events.Notifications.Time & The General Settings menu shall allow the user to set the default amount of time before the event to notify the user. \\
& \\
Settings.Events.Notifications. Time.Default & The default amount of time for a notification on an event shall be set to 5 minutes until changed by the user. \\
& \\
Settings.Events.Duration & The General Settings menu shall allow the user to set the default duration for a standard event. \\
& \\
Settings.Events.Duration.Default & The default duration for an event shall be set to 1 hour until changed by the user. \\
& \\
Settings.Events.Location & The General Settings menu shall allow the user to set a default location for when events are created. \\
& \\
Settings.Events.Location.Default & The default location for events shall be set to none until changed by the user. \\
\hline
Settings.Account.Login & The General Settings menu shall allow the user to login to their account. \\
& \\
Settings.Account.Logout & The General Settings menu shall allow the user to logout of their account. \\
& \\
Settings.Account.Register & The General Settings menu shall allow the user to create a new account and then login. \\
& \\
Settings.Account.View & The General Settings menu shall allow the user to view their account information (email and option to reset password) after logging in. \\
& \\
Settings.Account.ChangeEmail & The General Settings menu shall allow the user to change their account email after logging in. \\
& \\
Settings.Account.ResetPassword & The General Settings menu shall allow the user to reset the password for their account after logging in. \\
\hline
\end{longtable}
\end{center}

\section{Auto Scheduling}

\subsection{Description and Priority}
A user is able to create a Deadline Event or edit events such that they overlap.
When the user confirms these changes, the application will automatically reschedule
non-locked events, including any new Deadline Events being added such that events
do not conflict with each other and events occur at a valid location per the event.
If such a schedule is not found, the application will alert the user and will not
modify their schedule. When a new schedule has been created, the user may view a
graphical comparison with the old schedule and accept, modify, or reject it.
Priority=High.

\subsection{Stimulus/Response Sequences}
\begin{center}
\begin{tabular}{ p{2cm} p{13cm} }
Stimulus: & User adds Deadline events\\
Response: & Application searches for times that event blocks can be created for
the deadline event, moving non-locked events if needed.  All events must be valid
when rescheduling is finished.\\
\\
Stimulus: & User makes an edit which causes events to conflict.\\
Response: & Application leaves in place all events that were modified by the user
and attempts to reschedule conflicting events so that all events are valid.\\
\\
Stimulus: & A new schedule is generated by the Auto Scheduler\\
Response: & User is presented with a graphical comparison of their new and old
schedule and asked to either confirm, edit, or reject the schedule.\\
\\
Stimulus: & User accepts new schedule\\
Response: & The calendar is updated to reflect the new schedule.\\
\\
Stimulus: & User chooses to edit the new schedule\\
Response: & User is returned to edit mode with the new schedule and no changes
are made yet to the user calendar.\\
\\
Stimulus: & User rejects the new schedule\\
Response: & User is returned to their calendar and the new schedule changes
are thrown out.\\
\end{tabular}
\end{center}

\subsection{Functional Requirements}
\begin{center}
\begin{longtable}{ | p{6cm} | p{9cm} | }
\hline
Auto.Deadline & The auto scheduler must schedule time blocks for the user based on
the parameters given by a Deadline event\\
& \\
Auto.Deadline.Deadline & The auto scheduler must not schedule time blocks after the
User given deadline.\\
& \\
Auto.Deadline.TotalTime & The sum total time scheduled must be exactly equal to
the amount of time specified by the user.\\
& \\
Auto.Deadline.MinTime & The length of time that a time block is scheduled may not
be less than the minimum specified time by the user.\\
& \\
Auto.Deadline.MaxTime & The length of time that a time block is scheduled may not
be greater than the maximum specified time by the user.\\
& \\
Auto.Deadline.TimeBetween & There must be a time between blocks of the same event
specified by the Settings.AutoScheduling.MinOpenTime.\\
& \\
Auto.Deadline.Breaks & If specified by the user, time blocks must contain breaks
of a specified length such that there is no contiguous length of time greater
than specified by the user during which a block of the deadline event is scheduled
but no break is scheduled.  The algorithm must use the fewest number of breaks
possible.  Breaks count toward total block length, but do not contribute to the
total time of the deadline event.\\
\hline
Auto.Schedule & The auto scheduler must create a valid schedule.\\
& \\
Auto.Schedule.Deadline & All Deadline events in the schedule must conform to the
Auto.Deadline requirements.\\
& \\
Auto.Schedule.Conflicts & No non-location events may be scheduled at the same time\\
& \\
Auto.Schedule.Lock & Any events locked by the user may not be changed by the
auto scheduler.  All location events are treated as locked\\
& \\
Auto.Schedule.Location & Any events with a specified location must be scheduled
during corresponding location events\\
& \\
Auto.Schedule.MoveEvent & the auto scheduler may move events already scheduled by
the user as long as it conforms to the above requirements.\\
\hline
Auto.Diff & When the auto scheduler has created a valid schedule, the user is
presented with a graphical comparison of the new schedule with their current one
and asked if they want to accept it, edit it, or reject it.\\
& \\
Auto.Diff.Accept & If the user accepts the new schedule, the user's calendar is
updated to reflect these changes\\
& \\
Auto.Diff.Edit & If the user decides to edit the schedule, they are returned to
edit mode with the new schedule, but no changes are made to their calendar.\\
& \\
Auto.Diff.Reject & If the user rejects the schedule, they are returned to their
calendar view and the new schedule is thrown out with no changes being made to
their calendar.\\
\hline
\end{longtable}
\end{center}

\section{Inter-Device Synchronization}

\subsection{Description and Priority}
This feature allows the user to synchronize their schedule between devices.
This will be done by allowing the user to register an account with which they
can log into the application. The user's schedule will be associated with that
account. All updates the user makes on their current device will be sent to the
server, so that their changes will be pulled from the server when the user logs
in on a different device. Additionally, the user will be able to log out of
their account on their current device. This feature will be \textbf{medium} priority.

\subsection{Stimulus/Response Sequences}
\begin{center}
    \begin{tabular}{ p{2cm} p{13cm} }
    Stimulus: & User opens application\\
    Response: & Application opens login dialog box for the user to enter their user-name
    and password if the user is not already logged in.\\
    \\
    Stimulus: & User verifies login information\\
    Response: & If the information was correct, the user's schedule will be displayed.
    If not, the user will be informed it was incorrect and prompt for login information
    again.\\
    \\
    Stimulus: & User attempts to register account\\
    Response: & Application opens up a new prompt where the user may create a new
    account and register it with the server.\\
    \\
    Stimulus: & User edits schedule locally\\
    Response: & Application sends the updates to the server and applies changes to
    schedule on the server\\
    \\
    Stimulus: & User edits schedule on remote device\\
    Response: & Application receives the updates from the server and applies changes
    to the schedule on local device.\\
    \\
    Stimulus: & User logs out of application\\
    Response: & Application closes the schedule and redisplays the login dialog box.\\
    \end{tabular}
\end{center}

\subsection{Functional Requirements}
\begin{center}
    \begin{longtable}{ | p{6cm} | p{9cm} | }
    \hline
    Sync.Login & The application must prompt the user for their login information
    upon startup if they are not already logged in.\\
    & \\
    Sync.Login.User-name & The login dialog box must allow the user to type their
    user-name into a text field.\\
    & \\
    Sync.Login.Password & The login dialog box must allow the user to type their
    password into a text field while hiding their entry.\\
    & \\
    Sync.Login.Verify & The login dialog box must allow the user to verify their
    entered login information. Application will query the server for the
    user-name and password pair. If it was correct they will see their schedule,
    if not they will be prompted for their login information again.\\
    & \\
    Sync.Login.Register & The login dialog box must open a new dialog box to allow the
    user to create a new account and register it with the server\\
    \hline
    Sync.Update.Send & The application will send any updates made by the user to the
    server at a scheduled interval. The updates will be applied to the schedule on the server.\\
    & \\
    Sync.Update.Receive & The application will receive any updates made to the schedule
    on the server and update the schedule on the local device if the schedules are different.\\
    \hline
    Sync.Logout & The application will allow the user to log out of their account. The
    application then displays the login dialog box. While closing the previous schedule\\
    \hline
    \end{longtable}
\end{center}

\section{Editing Toolbar}

\subsection{Description and Priority}
This feature allows the user to edit their schedule directly in the application's
graphical display. There will be a toolbar providing the user with editing tools
such as drag and drop, re-size, cut, copy, paste, and add from existing. These editing
tools will be selected via the toolbar. Priority = High.

\subsection{Stimulus/Response Sequences}
\begin{center}
    \begin{tabular}{ p{2cm} p{13cm} }
    Stimulus: & User selects tool (clicking on tool's icon)\\
    Response: & Application registers subsequent clicks as using the selected tool and
    adjusts events accordingly.\\
    \\
    Stimulus: & User uses drag and drop tool (click event then hold+drag)\\
    Response: & Application adjusts corresponding event's start and end times. The event
    will be movable within a grid with cells corresponding to a specified time
    interval (for example 15 minute intervals)\\
    \\
    Stimulus: & User uses re-size tool (click event edge then hold+drag top or bottom edge)\\
    Response: & Application adjusts corresponding event's start time if the top
    edge was moved, end time if the bottom edge was moved. The edges will also be adjustable
    to the grid as mentioned in the drag and drop tool above.\\
    \\
    Stimulus: & User uses copy tool (click event)\\
    Response: & Application selects event for "copying". This original event is preserved.\\
    \\
    Stimulus: & User uses cut tool (click event)\\
    Response: & Application selects event for "cutting". This original event is removed.\\
    \\
    Stimulus: & User uses paste tool (click a new time slot)\\
    Response: & Application places a new copy of the event selected for "cutting" or "copying"
    in the time slot where the user clicks. Subsequent clicks add additional copies of the
    event. Only one event can be cut or copied at once.\\
    \\
    Stimulus: & User deselects tool (clicking on tool's icon again or selecting different tool)\\
    Response: & Application registers subsequent clicks as normal if tool's icon
    was clicked again. If new tool was selected, registers subsequent clicks as
    using the new tool.
    \end{tabular}
\end{center}
The user will select a tool on the toolbar by clicking the tool's corresponding icon
then apply the tool to events on the schedule. The user can then utilize the tools
by clicking on the events in their graphical user interface. The tools can be de-selected
by clicking on their icon in the toolbar.

\subsection{Functional Requirements}
\begin{center}
    \begin{longtable}{ | p{6cm} | p{9cm} | }
    \hline
    Toolbar.Select.DragDrop & The application registers the drag and drop tool
    as selected when the user clicks on the drag and drop icon in the toolbar.\\
    & \\
    Toolbar.Select.Re-size & The application registers the re-size tool as selected
    when the user clicks on the re-size icon in the toolbar.\\
    & \\
    Toolbar.Select.Cut & The application registers the cut tool
    as selected when the user clicks on the cut icon in the toolbar.\\
    & \\
    Toolbar.Select.Copy & The application registers the copy tool as selected
    when the user clicks on the copy icon in the toolbar.\\
    & \\
    Toolbar.Select.Paste & The application registers the paste tool as selected
    when the user clicks on the paste icon in the toolbar.\\
    \hline
    Toolbar.DragDrop & The application moves the start and end times to the new
    times specified by the user when the drag and drop tool is selected\\
    & \\
    Toolbar.DragDrop.Drag & The application moves the event in the graphical
    interface following the user's cursor after the event was clicked on and
    not released.\\
    & \\
    Toolbar.DragDrop.Release & The application moves the start and end times to
    the new times specified by the time slot the user released the event in.\\
    \hline
    Toolbar.Re-size & The application adjusts the duration of the specified event.\\
    & \\
    Toolbar.Re-size.DragEdge & The application moves the top or bottom edge
    of the event in the graphical interface when the edge was clicked and not
    released. The edge follows the cursor.\\
    & \\
    Toolbar.Re-size.Release & The application moves the start time to the new time
    specified by where the user released the top edge of the event. The end time
    will be moved if the bottom edge was released.\\
    \hline
    Toolbar.Copy & The application selects the event for "copying". The
    event remains unchanged.\\
    & \\
    Toolbar.Cut & The application selects the event for "cutting". The
    event is removed from the schedule.\\
    & \\
    Toolbar.Paste & The application creates a copy of the event selected
    for "cutting" or "copying" at the specified time slot. Only one
    event can be selected at a time.\\
    & \\
    \hline
    \end{longtable}
\end{center}

\section{Events}

\subsection{Description and Priority}
Events are blocks of time on the calendar with attached reminders as the time of the event approaches. Priority = High.

\subsection{Event Types}
\begin{center}
\begin{tabular}{ | p{5cm} | p{10cm} | }
\hline
Standard Event &
The default event type. This is locked by default.\\
\hline
Location Event &
The event type which denotes the location of the user is within its duration.\\
\hline
Deadline without Location &
The autoscheduler schedules times to work before this event happens. It takes as input
approximate working time as well as the standard event inputs.\\
\hline
Deadline with Location &
This is the same as the Deadline without Location, with the addition
that working time can only be scheduled when the user is within the duration of a certain named Location Event.\\
\hline
\end{tabular}
\end{center}

\subsection{Stimulus/Response Sequences}
\begin{center}
\begin{longtable}{ p{2cm} p{13cm} }
Stimulus: & The user clicks the button to create an event. \\
Response: & A form is opened which presents the user with the option to change the event characteristics and type.\\
\\
Stimulus: & The user chooses the option to finish the event creation form. \\
Response: & The application returns to the calendar view and creates an event as specified by the form. \\
\\
Stimulus: & The user double clicks or taps on an existing event. \\
Response: & The event editing form is opened. \\
\\
Stimulus: & The user exits the event editing form by clicking or tapping an "apply" button. \\
Response: & The event characteristics are changed and the event is moved on the calendar if necessary. \\
\\
Stimulus: & The user clicks or taps the delete button while an event is selected. \\
Response: & The application displays a popup which asks the user for confirmation. If the user confirms, the event is deleted. \\
\\
Stimulus: & The user drags an event to a place on the calendar. \\
Response: & The event snaps to the grid, avoiding overlap with other non-location event. \\
\end{longtable}
\end{center}

\subsection{Functional Requirements}
\begin{center}
\begin{longtable}{ | p{6cm} | p{9cm} | }
\hline
Event.TimePeriod & Event start and end times can be set. \\
\hline
Event.Location & Events can have a location attached to them. Location events must have this characteristic. \\
& \\
Event.Notifications & Events have editable notification settings (time before event, types of notification).\\
\hline
Event.Frequency & Events can be set to repeat after a set amount of time (weekly, monthy, yearly, etc.) \\
& \\
Event.Lock & Events can be set to be unable to be moved by the autoscheduler. \\
& \\
Event.Unlock & Events can set a range in which the autoscheduler can schedule them.\\
& \\
Event.Create & Events can be created on the calendar. \\
& \\
Event.Edit & Events can be opened for editing after creation. \\
& \\
Event.Delete & Events can be deleted from the calendar. \\
& \\
Event.Standard.StartTime & Events have a start time which can be adjusted in the editing form. \\
& \\
Event.Standard.EndTime & Events have an end time which can be adjusted in the editing form. \\
& \\
Event.Deadline.Deadline & Deadline Events have a deadline, before which all scheduled work for that deadline must be placed. \\
& \\
Event.Deadline.WorkTime & Deadline Events have a duration of time that they must schedule for work before the deadline time. \\

\hline
\end{longtable}
\end{center}

\chapter{Other Nonfunctional Requirements}

\section{Performance Requirements}
\begin{center}
\begin{tabular}{ p{1.5cm} p{13cm} }
PE-1: & The user interface must respond to input within 100ms in order to maintain
the feeling of user control and fluency\\
PE-2: & The application must take less than 5 seconds to load completely and allow
for interaction across all platforms on a 5Mbps connection.
\end{tabular}
\end{center}

\section{Safety Requirements}
No safety Requirements have been identified

\section{Security Requirements}
\begin{center}
\begin{tabular}{ p{1.5cm} p{13cm} }
SE-1: & All communication between the server and client must be encrypted over https.\\
SE-2: & Plaintext passwords must not be stored on the server and should only be
stored in the database after being salted and hashed.\\
SE-3: & Users may only see their own information including but not limited to calendar
events and personal info such as name and email unless granted permission by the owner.
No other parties may have access to this information.
\end{tabular}
\end{center}

\section{Software Quality Attributes}
\begin{center}
\begin{tabular}{ p{1.5cm} p{13cm} }
QA-1: & 75\% of users must be able to create any type of event and use any of the
toolbar options after completing the first time tutorial.\\
QA-2: & The application must conform to all Android and iOS app standards for the
respective versions of the app.\\
QA-3: & If the app is closed while editing, the user should be returned to the editing
mode with the changes that they had made upon reopening the app on the same device.\\
QA-4: & 60\% of code for the app on any platform must be shared between all platforms.
\end{tabular}
\end{center}

\section{Other Requirements}
\begin{center}
\begin{tabular}{ p{1.5cm} p{13cm} }
OT-1: & Any non user generated text displayed to the user must be referenced from
a locales file which can contain alternatives for supported languages.\\
\end{tabular}
\end{center}

\chapter{Appendix A: Glossary}
%see https://en.wikibooks.org/wiki/LaTeX/Glossary
$<$Define all the terms necessary to properly interpret the SRS, including
acronyms and abbreviations. You may wish to build a separate glossary that spans
multiple projects or the entire organization, and just include terms specific to
a single project in each SRS.$>$

\chapter{Appendix B: Analysis Models}
$<$Optionally, include any pertinent analysis models, such as data flow
diagrams, class diagrams, state-transition diagrams, or entity-relationship
diagrams.$>$

\chapter{Appendix C: To Be Determined List}
$<$Collect a numbered list of the TBD (to be determined) references that remain
in the SRS so they can be tracked to closure.$>$

\end{document}
